%% Submissions for peer-review must enable line-numbering
%% using the lineno option in the \documentclass command.
%%
%% Camera-ready submissions do not need line numbers, and
%% should have this option removed.
%%
%% Please note that the line numbering option requires
%% version 1.1 or newer of the wlpeerj.cls file, and
%% the corresponding author info requires v1.2

\documentclass[fleqn,10pt,lineno]{wlpeerj}

\title{\texttt{dms-view}: visualization tool for deep mutational scans}

\author[1, 2]{Sarah K. Hilton}
\author[1, 3]{John Huddleston}
\author[1, 4]{Allison Black}
\author[1, 2]{Khrystyna North}
\author[1]{Adam S. Dingens}
\author[1, 2, 4]{Trevor Bedford}
\author[1, 2]{Jesse D. Bloom}
\affil[1]{Computational Biology Program, Fred Hutch Cancer Research Center, Seattle, WA}
\affil[2]{Department of Genome Sciences, University of Washington, Seattle, WA}
\affil[3]{Molecular and Cellular Biology Program, University of Washington, Seattle, WA}
\affil[4]{Department of Epidemiology, University of Washington, Seattle, WA}
\corrauthor[1, 2]{Jesse D. Bloom}{jbloom@fredhutch.org}

% \keywords{Keyword1, Keyword2, Keyword3}

\begin{abstract}
Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text.
\end{abstract}

\begin{document}

\flushbottom
\maketitle
\thispagestyle{empty}

\section*{Introduction}

\section*{Data for case studies}\label{sec:data}

\section*{Website output and discussion}

\section*{How to upload your own data}

\section*{Conclusions}

\section*{Acknowledgments}

This work started as the final project for UW class CSE 512 Data Visualization as a part of the UW eScience Advanced Data Science Option curriculum.
SKH, JH, AB, and KN would like to thank to Dr. Jeffrey Heer, Halden Lin, and Jane Hoffswell for their input on the initial design.
SKH and JH would like to thank members of the Bloom and Bedford lab for helpful discussions and testing. 

\bibliography{refs}

\end{document}
